Treatment Outcome Visualization

### 2023-09-20 Treatment_Outcomes.Rmd
Pre/Post Scores!!
extra pre/post

### Extract pre/post scores
```{r}
# 1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.

Mothership_post <- Mothership %>%
  mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),

#2. Create pre_scores
      CUXOS_pre = Day1_CUXOS,
      CUDOS_pre = Day1_CUDOS
      ) %>%

#4. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_W)) %>%
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!Days_complete_1 > 40) %>%
  filter(!Days_complete_W == 0)

dim(Mothership_post)

#5. Then create df with CUDOS and CUXOS scores
  # Depression

    CUDOS_Score <- select(Mothership_post,
                      Day1_CUDOS:Day40_CUDOS)
    CUDOS_Score <- data.frame(CUDOS_Score)

  # Anxiety
    CUXOS_Score <- select(Mothership_post, Day1_CUXOS:Day40_CUXOS)
    CUXOS_Score <- data.frame(CUXOS_Score)

#6. Using incidences to extract values

Mothership_post <- Mothership_post %>%
  mutate(
    CUDOS_post = CUDOS_Score[cbind(c(1:8343),Mothership_post$Days_complete_W)],
    CUXOS_post = CUXOS_Score[cbind(c(1:8343),Mothership_post$Days_complete_W)]
  )

@@

```{r, include=FALSE}
# Try to extract values using a while loop?

for (i in 1:nrow(CUDOS_Score)){
  while(is.na(CUDOS_Score[i,CUDOS_Score$Days_complete_W])){
    x = Days_complete_W -1
    post_days <- CUDOS_Score[i,(x)]
  }
}
```

@@

ggplot(data=Pre_ANX,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#aeb6bf",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))

@@

ggplot(data=Pre_DEP,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#aeb6bf",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
       ylab = "Disorder Type")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))
```

>>>>

### Extract pre/post scores
```{r}
#1. load DF

Mothership

    Mothership_post <- Mothership |>
        filter(
          is.na(Prev_AdmitID_1),
          C_Admit_1 == 1
          ) |>
        mutate(
          dummy = -99
        )

    # Depressiopn
    CUDOS_Score_post <-  select(Mothership_post, dummy,Day1_CUDOS:Day40_CUDOS)
    # Anxiety
    CUXOS_Score_post <- select(Mothership_post, dummy,Day1_CUXOS:Day40_CUXOS)

#2. Getting post scores for people who have NA for post

    # Depression
    Post_DEP <- NA
    PD_df <- NA
    for(i in 1:nrow(CUDOS_Score_post)){
    PD_df <- unname(unlist(CUDOS_Score_post[i,]))
    PD_df <- PD_df[!is.na(PD_df)]
    PD_df <- tail(PD_df, n=1)
    Post_DEP <- rbind(Post_DEP,PD_df)
    }
    Post_DEP
    Post_Dep <- Post_DEP[-1]

    # Anxiety
    Post_ANX <- NA
    PA_df <- NA
    for(i in 1:nrow(CUXOS_Score_post)){
    PA_df <- unname(unlist(CUXOS_Score_post[i,]))
    PA_df <- PA_df[!is.na(PA_df)]
    PA_df <- tail(PA_df, n=1)
    Post_ANX <- rbind(Post_ANX,PA_df)
    }

    Post_ANX
    Post_anx <- Post_ANX[-1]

# 3. Getting BL scores for people who have NA at Baseline

    # Depression / Anxiety Dummy variable
    CUDOS_Score_pre <-  select(Mothership_post, Day1_CUDOS:Day40_CUDOS,dummy)
    CUXOS_Score_pre <- select(Mothership_post, Day1_CUXOS:Day40_CUXOS,dummy)

    # Depression
    Pre_DEP <- NA
    PD_df <- NA
    for(i in 1:nrow(CUDOS_Score_pre)){
    PD_df <- unname(unlist(CUDOS_Score_pre[i,]))
    PD_df <- PD_df[!is.na(PD_df)]
    PD_df <- head(PD_df, n=1)
    Pre_DEP <- rbind(Pre_DEP,PD_df)
    }
    Pre_dep <- Pre_DEP[-1]

    # Anxiety
    Pre_ANX <- NA
    PA_df <- NA
    for(i in 1:nrow(CUXOS_Score_pre)){
    PA_df <- unname(unlist(CUXOS_Score_pre[i,]))
    PA_df <- PA_df[!is.na(PA_df)]
    PA_df <- head(PA_df, n=1)
    Pre_ANX <- rbind(Pre_ANX,PA_df)
    }
    Pre_anx <- Pre_ANX[-1]

#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_pre = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
          CUDOS_pre = ifelse(CUDOS_pre < 0, NA, CUDOS_pre),
        CUXOS_pre = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
          CUXOS_pre = ifelse(CUXOS_pre < 0, NA, CUXOS_pre),
        CUDOS_post = ifelse(Post_Dep < 0, NA, Post_Dep),
        CUXOS_post = ifelse(Post_anx < 0, NA, Post_anx)
      )

@@

@@

"#aeb6bf"

ggplot(data=Pre_ANX,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUXOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))

@@

ggplot(data=Pre_DEP,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
       ylab = "Disorder Type")+
  scale_y_reverse(limits = c(45,15)) +
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))
```
